---
title: "wcs_2"
author: "Fiori Anglou"
date: "2024-06-05"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Data

```{r}
library(tidyverse)
post_syp_path <- "C:/Users/fa24575/Dropbox/Organic Waste Bans/06. Post SYP"
wcs <- read.csv(paste0(post_syp_path, "/03. Bans/wcs_2.csv"))
food_generators_MA <-  read.csv(paste0(post_syp_path, "/03. Bans/food_generators_MA.csv"))
food_generators_VT <-  read.csv(paste0(post_syp_path,"/03. Bans/food_generators_VT.csv"))
bans_thresholds <-  read.csv(paste0(post_syp_path,"/03. Bans/bans_thresholds.csv"))
processors <-read.csv(paste0(post_syp_path,"/03. Bans/food_processors_list_MA.csv"))
processors_VT <- read.csv(paste0(post_syp_path,"/03. Bans/food_processors_list_VT.csv"))
towns_coordinates_VT <- read.csv(paste0(post_syp_path,"/03. Bans/towns_coordinates_VT.csv"))

```


Exclude Oregon because (1) they report clean tons which is something that no other states does and (2) because their streams are also very different from everyone elses' and i do not know how to assign them 

# Setup 

## Function

```{r}
pre_processing_dt_state <- function (power2, year_cutoff)
{
  year_start <- 2006
  dt_state <- 
    power2 %>% 
    group_by (year, state_id, type) %>% 
    summarise(tons = sum(tons, na.rm=TRUE))%>% 
    filter(
      year >= year_start, 
      year <= year_cutoff, 
      type %in% c("disposal", "msw_disposed", "composting")
    ) %>%
    group_by(state_id) %>% 
    left_join (
      population %>% group_by(state_id, year) %>% summarise(state_pop = sum(pop)), 
      by = c("state_id", "year")
    ) %>%
    group_by(state_id, year, type) %>% 
    mutate(
      tons_pc = (tons/state_pop), 
      county_id = state_id
    ) %>% 
    group_by(state_id) %>% 
    mutate(n=n()) %>% 
    #filter(n == year_cutoff - year_start+1) %>% 
    select(-n) %>% 
    ungroup() 

  dt_state_initial <- dt_state
  return(dt_state_initial)
  
}
```


```{r}

wcs<-
  wcs %>% as_tibble() %>% 
  rename(
    activity = Activity, 
    jurisdiction = City
  ) %>% 
  mutate(
    activity = activity %>% str_to_lower,
    generator_category = generator_category %>% str_to_lower,
    material = material %>% str_to_lower, 
    tons = tons %>% as.numeric, 
    need_to_find = need_to_find %>% as.numeric

  ) %>% 
  filter(
  year >= 2000, year <=2022
  ) %>% 
  filter(
    state_id!="OR",
    !(state_id=="VT" & year==2013)
  )
# For Seattle, WA (state_id = M1) I have 1 residential WCS in 2014 and one commercial in 2016. I will have to use them both. I use year == 2015 


wcs <- wcs %>% mutate(year = ifelse(state_id == "M1", 2015, year)) 
```


### Total 

```{r}

wcs %>% 
  filter(generator_category=="all") %>% 
  filter(is.na(percentage)) %>% 
  group_by(year, state_id) %>% 
  pivot_wider(names_from=material, values_from=tons) %>% 
  mutate(
    compostable_paper = ifelse(is.na(compostable_paper), 0, compostable_paper),
    m=(food+yard_waste+compostable_paper)/total) %>% 
  select(m, state_id, year) %>% 
  filter(year>2005) %>% 
  ggplot(
    aes(x=year, y =m, color = state_id)
  ) +
  geom_line()+
  geom_point()

wcs %>% 
  filter(generator_category=="all") %>% 
  filter(!is.na(percentage)) %>% 
  group_by(year, state_id) %>% 
  pivot_wider(names_from=material, values_from=percentage) %>% 
  mutate(
    compostable_paper = ifelse(is.na(compostable_paper), 0, compostable_paper),
    m=(food+yard_waste+compostable_paper)) %>% 
  select(m, state_id, year) %>% 
  filter(year>2005) %>% 
  ggplot(
    aes(x=year, y =m, color = state_id)
  ) +
  geom_line()+
  geom_point()

```


## Need to find the percentage between commercial and residential

```{r}

wcs_ntf <- 
  wcs %>% 
  filter(!is.na(need_to_find), need_to_find!="") %>% 
  mutate(
    com_percentage = ifelse(state_id=="MA", 0.55, NA)
  ) %>% 
  filter(is.na(com_percentage)) %>% 
  select(
    state_id, year, generator_category, material, percentage, jurisdiction
  ) %>% 
  group_by(state_id, year, jurisdiction) %>% 
  pivot_wider(
    names_from = generator_category, 
    values_from = percentage
  ) %>% 
  mutate(
    implied_percentage = 1- (commercial-all)/(commercial-residential), 
    implied_percentage = ifelse(is.infinite(implied_percentage), 0.4, implied_percentage),
    implied_percentage = ifelse(implied_percentage>.9, 0.5, implied_percentage), 
    implied_percentage = ifelse(implied_percentage<0, 0.5, implied_percentage)
  ) %>% #filter(state_id=="WI") %>% 
  group_by(year, state_id, jurisdiction) %>% 
  summarise(
    implied_total = sum(all), 
    implied_com = sum(commercial*implied_percentage)/implied_total
  ) %>% 
  rbind(
    tibble(
      year= c(2010, 2013, 2016, 2019), 
      state_id = "MA", 
      jurisdiction = "Statewide", 
      implied_total = 1, 
      implied_com = 0.55
    )) %>% 
  select(-implied_total)

```

### Percentages 

```{r}
wcs_per <- 
  wcs %>%  
  filter(need_to_find!=1| is.na(need_to_find)) %>%
  filter(!is.na(percentage)) %>% 
  left_join(
    wcs_ntf, by = c("state_id", "year", "jurisdiction")
  ) %>% 
  filter(generator_category == "commercial"| state_id == "MA") %>% 
  mutate(
    final_percentage = implied_com * percentage
  ) %>% 
  select(state_id, year, jurisdiction, material, final_percentage, implied_com) %>% 
  pivot_wider(
    names_from=material, values_from = final_percentage) %>% 
  rename(
    total_com = implied_com
  )
```

### Tonnages 

```{r}

vt_food_total <- wcs %>% filter(state_id=="VT", year==2018, generator_category=="all") %>%
  filter(material=="food") %>% pluck("tons")/wcs %>% filter(state_id=="VT", year==2018, generator_category=="all") %>%  filter(material=="total") %>% pluck("tons")
  

wcs_tn <- 
  wcs %>%  
  filter(need_to_find!=1 | is.na(need_to_find)) %>%
  filter(!is.na(tons)) %>% 
  select(state_id, year, jurisdiction, generator_category, material, tons) %>% 
  mutate(
    generator_category_ind = ifelse(generator_category=="all", 1, 0)
  ) %>% 
  group_by(state_id, year, jurisdiction) %>%
  filter(n_distinct(generator_category)>1) %>% 
  group_by(state_id, year, jurisdiction, generator_category) %>%
  mutate(
    total_category = max(tons)
  ) %>% 
  group_by(state_id, year, jurisdiction) %>%
  mutate(
    total_all = max(tons)
  ) %>% 
  filter(generator_category %in% c("commercial", "self_haul")) %>% 
  group_by(state_id, year, jurisdiction, material) %>% 
  summarise(
    total_com = sum(total_category)/mean(total_all), 
    per = sum(tons) / mean(total_all)
  ) %>% 
  select(
    state_id, year, jurisdiction, per, total_com, material
  ) %>% 
  filter(material!="total") %>% 
  pivot_wider(
    names_from = material, values_from = per
  )
```

### Bargraph 

```{r}
wcs_plot <- 
  rbind(
    wcs_tn, 
    wcs_per
  )%>% filter(state_id!="M1")%>%
  select(
    state_id, year, jurisdiction, total_com, compostable_paper, yard_waste, food
  ) %>% 
  mutate(
    total_com = total_com - ifelse(is.na(compostable_paper), 0, compostable_paper)-food-yard_waste
  ) %>% 
  pivot_longer(
    cols = c("total_com" , "compostable_paper", "food", "yard_waste"), 
    names_to = "share", 
    values_to = "percentage"
  ) %>% 
  mutate(
    share = factor(
      share,
      levels = c("total_com","compostable_paper", "yard_waste", "food")
    ),
    share = share %>% 
      fct_recode(
        `Other` = "total_com", 
        Food = "food", 
        `Yard Waste` = "yard_waste", 
        `Compostable Paper` = "compostable_paper"
      )
  ) %>% 
  filter(
    year >=2006, year <2020#, state_id!="M1"
  ) %>% 
  group_by(
    state_id, share
  ) %>% 
  summarise(
    percentage = mean(percentage), 
    year= 1
  ) %>% 
  #filter(share!="Other") %>% 
  ggplot()+
  aes(fill=share, y=100*percentage, x= as.factor(year))+
  geom_bar(position="stack", stat="identity") +
  facet_grid(cols = vars(state_id))+
  scale_fill_grey(start = 0.9, end =0.3, guide = guide_legend(reverse = TRUE))+
  scale_y_continuous(breaks=c(seq(0,60, by =10)))+
  labs (x="", y="Fraction of total landfilled MSW (%)", fill = "Commercial:")+
  theme(
    panel.border = element_blank(),
    legend.position = "bottom", 
    panel.background = element_blank(),
    axis.ticks.x = element_blank(), 
    axis.text.x=element_blank(),
    text = element_text(family="Helvetica",size = 14, color = ut_colors[4]), 
    legend.title = element_text(family="Helvetica",size = 14, color = ut_colors[4]), 
    legend.text = element_text(family="Helvetica",size = 14, color = ut_colors[4]), 
    strip.background = element_blank(), 
    legend.key = element_blank())



ggsave(wcs_plot, filename = "wcs_plot.pdf", device = cairo_pdf,
       path= figure_path,
       width = 12, height = 5, units = "in")



rbind(
  wcs_tn, 
  wcs_per
)%>% 
  filter(jurisdiction=="Statewide") %>% 
  select(
    state_id, year, jurisdiction, total_com, compostable_paper, yard_waste, food
  ) %>% 
  mutate(
    total_com = total_com - ifelse(is.na(compostable_paper), 0, compostable_paper)-food-yard_waste
  ) %>% 
  pivot_longer(
    cols = c("total_com" , "compostable_paper", "food", "yard_waste"), 
    names_to = "share", 
    values_to = "percentage"
  ) %>% 
  mutate(
    share = factor(
      share,
      levels = c("total_com","compostable_paper", "yard_waste", "food")
    ),
    share = share %>% 
      fct_recode(
        `Other` = "total_com", 
        Food = "food", 
        `Yard Waste` = "yard_waste", 
        `Compostable Paper` = "compostable_paper"
      )
  ) %>% 
  filter(
    year >=2006, year <2022#, state_id!="M1"
  ) %>% 
  group_by(
    year, share
  ) %>% 
  summarise(
    percentage=mean(percentage, na.rm=TRUE), 
    state_id=1
  ) %>% 
  filter(share!="Other") %>% 
  ggplot()+
  aes(fill=share, y=100*percentage, x= as.factor(state_id))+
  geom_bar(position="stack", stat="identity") +
  facet_grid(cols = vars(year))+
  scale_fill_grey(start = 0.9, end =0.3, guide = guide_legend(reverse = TRUE))+
  scale_y_continuous(breaks=c(seq(0,60, by =10)))+
  labs (x="", y="Fraction of total landfilled MSW (%)", fill = "Commercial:")+
  theme(
    panel.border = element_blank(),
    legend.position = "bottom", 
    panel.background = element_blank(),
    axis.ticks.x = element_blank(), 
    axis.text.x=element_blank(),
    text = element_text(family="Helvetica",size = 14, color = ut_colors[4]), 
    legend.title = element_text(family="Helvetica",size = 14, color = ut_colors[4]), 
    legend.text = element_text(family="Helvetica",size = 14, color = ut_colors[4]), 
    strip.background = element_blank(), 
    legend.key = element_blank())
```



```{r}
rbind(
  wcs_tn, 
  wcs_per
)%>% 
  filter(jurisdiction=="Statewide") %>% 
  select(
    state_id, year, jurisdiction, total_com, compostable_paper, yard_waste, food
  ) %>% 
  mutate(
    total_com = total_com - ifelse(is.na(compostable_paper), 0, compostable_paper)-food-yard_waste
  ) %>% 
  pivot_longer(
    cols = c("total_com" , "compostable_paper", "food", "yard_waste"), 
    names_to = "share", 
    values_to = "percentage"
  ) %>% 
  mutate(
    share = factor(
      share,
      levels = c("total_com","compostable_paper", "yard_waste", "food")
    ),
    share = share %>% 
      fct_recode(
        `Other` = "total_com", 
        Food = "food", 
        `Yard Waste` = "yard_waste", 
        `Compostable Paper` = "compostable_paper"
      )
  ) %>% 
  filter(
    year >=2006, year <2020#, state_id!="M1"
  ) %>% 
  group_by(
    state_id, share
  ) %>% 
  mutate(
    n = n()
  ) %>% 
  group_by(state_id, share) %>% 
  mutate(
    n_wcs = 1:n()#ifelse(year/min(year)==1, 1, 2)
  ) %>% 
  filter(share!="Other") %>% 
  ggplot()+
  aes(fill=share, y=100*percentage, x= as.factor(n_wcs))+
  geom_bar(position="stack", stat="identity") +
  facet_grid(cols = vars(state_id), rows=vars(n))+
  scale_fill_grey(start = 0.9, end =0.3, guide = guide_legend(reverse = TRUE))+
  scale_y_continuous(breaks=c(seq(0,60, by =10)))+
  labs (x="", y="Fraction of total landfilled MSW (%)", fill = "Commercial:")+
  theme(
    panel.border = element_blank(),
    legend.position = "bottom", 
    panel.background = element_blank(),
    axis.ticks.x = element_blank(), 
    axis.text.x=element_blank(),
    text = element_text(family="Helvetica",size = 14, color = ut_colors[4]), 
    legend.title = element_text(family="Helvetica",size = 14, color = ut_colors[4]), 
    legend.text = element_text(family="Helvetica",size = 14, color = ut_colors[4]), 
    strip.background = element_blank(), 
    legend.key = element_blank())
```








```{r}
rbind(
  wcs_tn, 
  wcs_per
) %>% 
group_by(year) %>% 
  summarise(
    mean(food+yard_waste+compostable_paper, na.rm = TRUE), 
    n()
  )

rbind(
  wcs_tn, 
  wcs_per
) %>% 
group_by(year) %>% 
  summarise(
    mean(food, na.rm = TRUE), 
    n()
  )


rbind(
  wcs_tn, 
  wcs_per
) %>% 
  filter(year>=2020)


rbind(
  wcs_tn, 
  wcs_per
) %>% 
  filter(state_id=="WA")
```

# Expected effects 

## Covered materials
```{r}

rbind(
  rbind(
    wcs_tn, 
    wcs_per
  ) %>% 
    filter(state_id=="CA", year==2014) %>% 
    mutate(covered = food+compostable_paper  +yard_waste), 
  rbind(
    wcs_tn, 
    wcs_per
  ) %>% 
    filter(state_id=="MA", year==2013) %>% 
    mutate(covered = food), 
  rbind(
    wcs_tn, 
    wcs_per
  ) %>% 
    filter(state_id=="CT", year==2015) %>% 
    mutate(covered = food+compostable_paper  ), 
  rbind(
    wcs_tn, 
    wcs_per
  ) %>% 
    filter(state_id=="VT", year==2018)%>% 
    mutate(covered = food),
  rbind(
    wcs_tn, 
    wcs_per
  ) %>% 
    filter(state_id=="RI", year==2015) %>% 
    mutate(covered = food)
) %>% 
  ungroup %>% 
  select(state_id, covered)



```

## Thresholds & Covered Percentages

```{r}

#Thresholds
disposal_effect_size2 <- 
  rbind(
  tibble(
    year = seq(2014,2022), 
    state_id = "VT",
    threshold = c(104, 52, 26, rep(18, 3), rep(0,3)), 
  ) %>% 
    mutate(distance_threshold = ifelse(year<2020, 20, Inf)), 
  tibble(
    year = seq(2014,2022), 
    state_id = "CT",
    threshold = c(rep(104,6), rep(52, 3)), 
  ) %>% 
    mutate(distance_threshold = ifelse(year<2023, 20, Inf)), 
  tibble(
    year = seq(2014,2022), 
    state_id = "MA",
    threshold = c(rep(52,8), 26), 
    distance_threshold = Inf
  ) ,
  tibble(
    year = seq(2016,2022), 
    state_id = "RI",
    threshold = c(rep(104,2), rep(52, 4), 30), 
    distance_threshold = 15
  ),
  tibble(
    year = seq(2016,2022), 
    state_id = "CA",
    threshold = c(rep(52,1), rep(26, 2), rep(13, 4)), 
    distance_threshold = Inf
  ) 
) %>% 
  left_join(
    #Covered percentages
    food_generators_MA %>% as_tibble %>% 
      expand_grid(threshold = c(104, 52,30,  26, 18, 13, 0)) %>% 
      mutate(
        cover = ifelse(tons >= threshold, 1, 0)
      ) %>% 
      filter(!is.na(tons)) %>% 
      group_by(Type, cover,threshold) %>%
      summarise(tons = sum(tons)) %>% 
      mutate(total_tons_category = sum(tons)) %>% 
      ungroup %>% group_by(cover, threshold) %>% 
      mutate(total_tons_covered = sum(tons)) %>% 
      ungroup %>% group_by(threshold) %>% 
      mutate(total_tons = sum(tons), percentage = total_tons_covered/total_tons) %>%  filter(cover==1) %>% group_by(threshold) %>% 
      summarise(pc = mean(percentage)) %>% 
      cbind(  
        food_generators_VT %>% as_tibble %>% 
          mutate(tons = TonsPerWeek*52, town_name = str_to_lower(Town)) %>% 
          select(ID, town_name, tons) %>% 
          expand_grid(threshold = c(104, 52,30,  26, 18, 13, 0)) %>% 
          filter(!is.na(tons)) %>%        
          mutate(
            cover = ifelse(tons >= threshold, 1, 0)
          ) %>% group_by(cover, threshold) %>% 
          summarise(tons = sum(tons)) %>% 
          group_by(threshold) %>%
          mutate(total_tons = sum(tons)) %>% 
          filter(cover==1) %>% 
          mutate(pc=tons/total_tons) %>% 
          ungroup %>%  select(pc) %>% rename(pc_VT=pc)
      ), 
    by ="threshold"
  ) %>% 
  #Distance thresholds
  rowwise %>% 
  mutate(
    distance_MA = exempt_MA(distance_threshold, threshold), 
    distance_VT = exempt_VT(distance_threshold, threshold)
  ) %>% 
  ungroup %>% 
  mutate(
    pc = pc*distance_MA,
    pc2 = pc_VT*distance_VT
    # effect_2 = effect_2 * distance_MA,
    # effect_VT = effect_VT * distance_VT 
    # #effect_2 = ifelse(state_id=="VT", effect_VT, effect2)
  ) 



food_generators_MA %>% as_tibble() %>% filter(str_detect(Name, "Whole Foods")) %>% summarise(median(tons, na.rm=TRUE))

food_generators_MA %>% as_tibble() %>% filter(str_detect(Name, "Starbucks")) %>% summarise(median(tons, na.rm=TRUE))

food_generators_MA %>% as_tibble() %>% filter(str_detect(Name, "Applebee")) %>% summarise(median(tons, na.rm=TRUE))
```


## Expected Effects

```{r}
disposal_effect_size2 <- 
  rbind(
    rbind(
      wcs_tn, 
      wcs_per
    ) %>% 
      filter(state_id=="CA", year==2014) %>% 
      mutate(covered = food+compostable_paper  +yard_waste), 
    rbind(
      wcs_tn, 
      wcs_per
    ) %>% 
      filter(state_id=="MA", year==2013) %>% 
      mutate(covered = food), 
    rbind(
      wcs_tn, 
      wcs_per
    ) %>% 
      filter(state_id=="CT", year==2015) %>% 
      mutate(covered = food+compostable_paper  ), 
    rbind(
      wcs_tn, 
      wcs_per
    ) %>% 
      filter(state_id=="VT", year==2018)%>% 
      mutate(covered = food),
    rbind(
      wcs_tn, 
      wcs_per
    ) %>% 
      filter(state_id=="RI", year==2015) %>% 
      mutate(covered = food)
  ) %>% 
  ungroup %>% 
  select(state_id, covered) %>% 
  left_join(
    disposal_effect_size2, by = "state_id"
  ) %>% 
  mutate(
    covered = ifelse(state_id=="VT" & year > 2019, vt_food_total, covered)
  ) %>% 
  mutate(
    effect_size = covered * pc
  ) #%>% 
  #select(
  #  state_id, year, threshold, pc, effect_size
  #) #%>% filter(year<=2018) %>% group_by(state_id) %>% summarise(mean(exp_effect))


#write.csv(disposal_effect_size2, "disposal_effect_size2.csv", row.names=FALSE) 

```
### CT's robustness check
```{r}

state_id_given <- "VT"
distance_threshold <- 20
cities %>% 
  filter(
    state_id==state_id_given
  ) %>% 
  group_by(city, state_id, population) %>% 
  summarise(
    long_gen = unique(lng),
    lat_gen = unique(lat)
  ) %>%
  rename (
    pop_city = population
  ) %>% 
  left_join(
    power2 %>% 
      as_tibble() %>% 
      filter(
        type=="disposal", 
        year==2014, 
        state_id == state_id_given) %>% group_by(year, state_id, type) %>% summarise(tons = sum(tons)),
    by= c("state_id")) %>% 
  group_by(state_id) %>%  
  mutate(
    total_pop = sum(pop_city), 
    weight = tons * pop_city/total_pop) %>% expand_grid(
      composting_all_facilities %>% 
        filter(state_id==state_id_given) %>%
        select(composting_facility, long, lat) %>% 
        rename(
          long_pro = long, 
          lat_pro = lat
        )) %>% 
  mutate(
    lat_gen = lat_gen*pi/180,
    long_gen = long_gen*pi/180,
    lat_pro = lat_pro*pi/180,
    long_pro = long_pro*pi/180, 
    delta_lat = lat_gen-lat_pro, 
    delta_long = long_gen - long_pro, 
    a = sin(delta_lat / 2)^2 + cos(lat_gen) * cos(lat_pro) * sin(delta_long / 2)^2, 
    c = 2 * atan2(sqrt(a), sqrt(1 - a)), 
    distance = 3959*c
  ) %>% 
  select(year, state_id, weight, distance) %>% 
  group_by(weight) %>% 
  summarise(
    min_distance = min(distance, na.rm=TRUE)) %>% 
  ungroup %>% 
  filter(!is.na(weight)) %>%
  filter(min_distance < 100) %>% 
  mutate(ind = ifelse(min_distance <= distance_threshold, 1, 0)) %>% 
  group_by(ind) %>% 
  summarise(weight=sum(weight)) %>% 
  ungroup %>% 
  mutate(
    total = sum(weight),
    frac = weight/total) %>% 
  filter(ind ==1) %>% 
  mutate(
    covered=disposal_effect_size2 %>% filter(state_id==state_id_given, year <=2018) %>% summarise(covered=unique(covered)) %>%  pluck("covered"), 
    pc = disposal_effect_size2 %>% filter(state_id==state_id_given, year <=2018) %>% summarise(pc=mean(pc/distance_MA)) %>%  pluck("pc"),
    effect= covered*pc*frac
  )
  

```



## Municipal

```{r}


wcs_tn_muni <- 
  wcs %>%  
  filter(need_to_find!=1 | is.na(need_to_find)) %>%
  filter(!is.na(tons)) %>% 
  select(state_id, year, jurisdiction, generator_category, material, tons) %>% 
  mutate(
    generator_category_ind = ifelse(generator_category=="all", 1, 0)
  ) %>% 
  group_by(state_id, year, jurisdiction) %>%
  filter(n_distinct(generator_category)>1) %>% 
  group_by(state_id, year, jurisdiction, generator_category) %>%
  mutate(
    total_category = max(tons)
  ) %>% 
  group_by(state_id, year, jurisdiction) %>%
  mutate(
    total_all = max(tons)
  ) %>% 
  filter(generator_category %in% c("commercial", "self_haul", "residential")) %>% 
  group_by(state_id, year, jurisdiction, material) %>% 
  summarise(
    total_com = sum(total_category)/mean(total_all), 
    per = sum(tons) / mean(total_all)
  ) %>% 
  select(
    state_id, year, jurisdiction, per, total_com, material
  ) %>% 
  filter(material!="total") %>% 
  pivot_wider(
    names_from = material, values_from = per
  ) %>% 
  filter(jurisdiction %in% c("Boulder", "Seattle"))


municipal <- read.csv("municipal_effect.csv")

#Covers residents and 
municipal <- 
  rbind(
    seattle %>%  
      filter(
        year == 2014 #year before the ban
      ) %>%  
      select(year, state_id, county_id, tons_pc, tons, type), 
    boulder %>%  
      filter(
        year == 2015 #year before the ban
      ) %>%  
      select(year, state_id, county_id, tons_pc, tons, type)
  ) %>% 
  left_join(
    wcs_tn_muni %>%
      group_by(state_id) %>% 
      filter(year ==max(year)) %>% 
      select(-year) %>%  
      filter(state_id %in% c("M1")| jurisdiction == "Boulder") %>% 
      mutate(state_id = ifelse(jurisdiction == "Boulder", "M2", state_id)), #basically assume that percentages hold
    by = c("state_id")
  ) %>% 
  filter(type %in% c("disposal", "composting")) %>% 
  mutate(
    compostable_paper = tons*(compostable_paper+food+yard_waste),
    food = tons*food
  ) %>% 
  group_by(year, state_id, type) %>% 
  summarise(
    tons= mean(tons),
    compostable_paper = sum(compostable_paper), 
    food = sum(food)
  ) %>% ungroup %>% 
  mutate(
    compostable_paper = compostable_paper/tons,
    food = food/tons, 
    disposal_effect = ifelse(state_id == "M1", food, compostable_paper)
    #in seattle the law covers foods 
    #in Boulder (M2) it covers composting materials: here I use compostable paper + food
  ) %>% 
  select(year, state_id, type, disposal_effect, tons) %>% 
  pivot_wider(names_from = type, values_from = tons) %>% 
  group_by(year, state_id) %>% 
  summarise(disposal_effect=mean(disposal_effect), composting = mean(composting, na.rm=TRUE), disposal = mean(disposal, na.rm=TRUE)) %>% 
  mutate(
    composting_effect = disposal_effect* disposal*0.5/ composting
  ) %>% 
  pivot_longer(
    cols = c("composting", "disposal"), 
    names_to = "type", 
    values_to = "tons"
  ) %>% 
  mutate(
    effect = ifelse(type == "disposal", -disposal_effect, composting_effect)
  ) %>% 
  ungroup %>% 
  select(
    state_id, type, effect
  ) %>% rbind(tibble(state_id = "M3", type="disposal", effect = -0.268-0.094))

write.csv(municipal, "municipal_effect.csv", row.names = FALSE)

```


## Composting effect

```{r}

disposal_effect_size <- read.csv("disposal_effect_size2.csv")


composting_effect <- 
  disposal_effect_size %>% 
  as_tibble %>% 
  left_join(
    power2 %>% group_by(state_id, year, type) %>% summarise(tons = sum(tons)) %>%  filter(type=="composting") %>% select(tons, year, state_id), by = c("year", "state_id")) %>%
  filter(!is.na(tons)) %>% rename(composting =tons) %>% 
  left_join(
    power2 %>%  group_by(state_id, year, type) %>% summarise(tons = sum(tons)) %>% filter(type=="disposal") %>% select(tons, year, state_id), by = c("year", "state_id")) %>%
  group_by(state_id) %>% select(state_id, year, composting, tons, effect_size) %>% 
  mutate(
    tons = ifelse(year==2014, tons, NA), 
    composting = ifelse(year==2014, composting, NA), 
    tons = mean(tons, na.rm=TRUE),
    composting = mean(composting, na.rm=TRUE),
    composting_effect = effect_size* tons*0.5/ composting
  ) %>% ungroup %>% select(state_id, year, effect_size, composting_effect)
  

write.csv(composting_effect, "composting_effect.csv", row.names = FALSE)
```


## Plot
```{r}

disposal_effect_size2 <- read.csv("disposal_effect_size2.csv")

disposal_effect_size_plot <-
  disposal_effect_size2 %>% 
  group_by(state_id) %>% 
  mutate(
    effect_size = ifelse(is.na(effect_size), max(effect_size, na.rm=TRUE), effect_size),
    label_x = ifelse(year== max(year), year+0.2, NA),
    label_y = ifelse(year== max(year), effect_size, NA),
    label_y = ifelse(state_id == "MA", label_y-0.01, label_y),
    label_y = ifelse(state_id == "CT", label_y+0.01, label_y)
  ) %>%
  ggplot(aes(x=year, y=-100*effect_size, color = state_id))+  
  geom_line(size=0.5)+
  labs(x="", y = "Expected Effect Size (%)", subtitle = "State-Level")+
  geom_text(aes(x=label_x, y = -100*label_y, label = state_id), family="Helvetica", size = 3)+
  geom_hline(yintercept = -10, color = ut_colors[5], linetype="dotted", size =0.3)+
  geom_hline(yintercept = -20, color = ut_colors[5], linetype="dotted", size =0.3)+
  geom_hline(yintercept = -30, color = ut_colors[5], linetype="dotted", size =0.3)+
  scale_color_manual(values=rep('seagreen', 5))+
  scale_x_continuous(breaks = c(2014:2022))+
  scale_y_continuous(breaks = c(seq(0, -40, by = -10)), limits= c(-45,0))+
  theme(
    legend.position = "none", 
    panel.background = element_blank(),
    legend.text=element_text(family = "Helvetica",size=12, color = ut_colors[4]),
    text = element_text(family = "Helvetica", size = 12, color = ut_colors[4]), 
    plot.title = element_text(hjust = 0.5, family = "Helvetica", size = 12, color = ut_colors[4]),
    axis.ticks.x = element_line(size = 0.1)
  ) 


disposal_effect_size_plot_muni <- 
  municipal %>% #this comes from the WCS script
  filter(type == "disposal") %>%
  expand_grid(year= 2009:2022)%>%
  mutate(
    effect_size = ifelse(state_id =="M1" & year < 2015, NA, ifelse(state_id == "M2" & year < 2016, NA, effect)),
    state_id = ifelse(state_id == "M1", "Seattle, WA", ifelse(state_id=="M2","Boulder, CO", "San Francisco, CA")),
    label_x = ifelse(year== max(year), year-2, NA),
    label_y = ifelse(year== max(year), effect_size- 0.02, NA), 
    effect_size = - effect_size
  ) %>%
  ggplot(aes(x=year, y=-100*effect_size, color = state_id))+    
  geom_line(size=0.5)+
  labs(x="", y = "", subtitle = "City-Level")+
  geom_text(aes(x=label_x, y = 100*label_y, label = state_id), family="Helvetica", size = 3)+
  geom_hline(yintercept = -10, color = ut_colors[5], linetype="dotted", size =0.3)+
  geom_hline(yintercept = -20, color = ut_colors[5], linetype="dotted", size =0.3)+
  geom_hline(yintercept = -30, color = ut_colors[5], linetype="dotted", size =0.3)+
  scale_color_manual(values=rep('seagreen', 3))+
  scale_x_continuous(breaks = c(seq(2009,2022, by = 2)))+
  scale_y_continuous(breaks = c(seq(0, -40, by = -5)), limits= c(-45,0))+
  theme(
    legend.position = "none", 
    panel.background = element_blank(),
    #plot.title = element_text(hjust = 0.5, size=10),
    legend.text=element_text(family = "Helvetica",size=12, color = ut_colors[4]),
    #plot.caption = element_text(hjust=0.5,size = 10)
    text = element_text(family = "Helvetica", size = 12, color = ut_colors[4]), 
    plot.title = element_text(hjust = 0.5, family = "Helvetica", size = 12, color = ut_colors[4]), 
    axis.ticks.y = element_blank(), 
    axis.text.y =  element_blank(),
    axis.ticks.x = element_line(size = 0.1)
  )  


disposal_effect_size_plot <- ggpubr::ggarrange(disposal_effect_size_plot, disposal_effect_size_plot_muni, ncol=2, widths = c(1, 1))

ggsave(disposal_effect_size_plot, filename = "disposal_effect_size.pdf", device = cairo_pdf,
       path= figure_path,
       width = 9, height = 3.25, units = "in")

disposal_effect_size_plot <-
  disposal_effect_size2 %>% 
  group_by(state_id) %>% 
  mutate(
    effect_size = ifelse(is.na(effect_size), max(effect_size, na.rm=TRUE), effect_size),
    label_x = ifelse(year== max(year), year+0.2, NA),
    label_y = ifelse(year== max(year), effect_size, NA),
    label_y = ifelse(state_id == "MA", label_y-0.01, label_y),
    label_y = ifelse(state_id == "CT", label_y+0.01, label_y)
  ) %>%
  ggplot(aes(x=year, y=-100*effect_size, color = state_id, size=state_id))+
  geom_line()+
  labs(x="", y = "Expected Effect Size (%)", subtitle = "State-Level")+
  geom_text(aes(x=label_x, y = -100*label_y, label = state_id), family="Helvetica", size = 3)+
  geom_hline(yintercept = -10, color = ut_colors[5], linetype="dotted", size =0.3)+
  geom_hline(yintercept = -20, color = ut_colors[5], linetype="dotted", size =0.3)+
  geom_hline(yintercept = -30, color = ut_colors[5], linetype="dotted", size =0.3)+
  scale_color_manual(values=c(rep(ut_colors[5], 4), "seagreen"))+
  scale_size_manual(values=c(rep(0.5, 4),1))+
  scale_x_continuous(breaks = c(2014:2022))+
  scale_y_continuous(breaks = c(seq(0, -40, by = -10)), limits= c(-45,0))+
  theme(
    legend.position = "none", 
    panel.background = element_blank(),
    legend.text=element_text(family = "Helvetica",size=12, color = ut_colors[4]),
    text = element_text(family = "Helvetica", size = 12, color = ut_colors[4]), 
    plot.title = element_text(hjust = 0.5, family = "Helvetica", size = 12, color = ut_colors[4]),
    axis.ticks.x = element_line(size = 0.1)
  ) 


disposal_effect_size_plot_muni <- 
  municipal %>% #this comes from the WCS script
  filter(type == "disposal") %>%
  expand_grid(year= 2009:2022)%>%
  mutate(
    effect_size = ifelse(state_id =="M1" & year < 2015, NA, ifelse(state_id == "M2" & year < 2016, NA, effect)),
    state_id = ifelse(state_id == "M1", "Seattle, WA", ifelse(state_id=="M2","Boulder, CO", "San Francisco, CA")),
    label_x = ifelse(year== max(year), year-2, NA),
    label_y = ifelse(year== max(year), effect_size- 0.02, NA), 
    effect_size = - effect_size
  ) %>%
  ggplot(aes(x=year, y=-100*effect_size, color = state_id))+
  geom_line(size=0.5)+
  labs(x="", y = "", subtitle = "City-Level")+
  geom_text(aes(x=label_x, y = 100*label_y, label = state_id), family="Helvetica", size = 3)+
  geom_hline(yintercept = -10, color = ut_colors[5], linetype="dotted", size =0.3)+
  geom_hline(yintercept = -20, color = ut_colors[5], linetype="dotted", size =0.3)+
  geom_hline(yintercept = -30, color = ut_colors[5], linetype="dotted", size =0.3)+
  scale_color_manual(values=rep(ut_colors[5], 3))+
  scale_x_continuous(breaks = c(seq(2009,2022, by = 2)))+
  scale_y_continuous(breaks = c(seq(0, -40, by = -5)), limits= c(-45,0))+
  theme(
    legend.position = "none", 
    panel.background = element_blank(),
    #plot.title = element_text(hjust = 0.5, size=10),
    legend.text=element_text(family = "Helvetica",size=12, color = ut_colors[4]),
    #plot.caption = element_text(hjust=0.5,size = 10)
    text = element_text(family = "Helvetica", size = 12, color = ut_colors[4]), 
    plot.title = element_text(hjust = 0.5, family = "Helvetica", size = 12, color = ut_colors[4]), 
    axis.ticks.y = element_blank(), 
    axis.text.y =  element_blank(),
    axis.ticks.x = element_line(size = 0.1))

disposal_effect_size_plot <- ggpubr::ggarrange(disposal_effect_size_plot, disposal_effect_size_plot_muni, ncol=2, widths = c(1, 1))

ggsave(disposal_effect_size_plot, filename = "disposal_effect_size_VT.pdf", device = cairo_pdf,
       path= figure_path,
       width = 9, height = 3.25, units = "in")
```


# Rob Checks for R4
## Smallest detectable share

```{r}
disposal_effect_size2 %>%
  select(
    state_id, year, threshold, pc, covered, effect_size
  ) %>% 
  left_join(
    bt_with_power_data %>% select(state_id, power_low) %>% 
      filter(state_id%in% c("CA", "CT", "MA", "VT", "RI")), 
      by = c("state_id")
  ) %>% 
  filter(year < 2019) %>% 
  group_by(state_id, covered, power_low) %>% 
  summarise(
    mean_coverage = mean(pc), 
    avg_exp_effect =mean(effect_size)
    ) %>% 
  mutate(
    power_low = -power_low/100, 
    min_fraction = power_low/mean_coverage, 
    percent_difference = (covered-min_fraction)/covered,
    pp_difference = covered-min_fraction
  )
```



## Do other states change as much? 

```{r}
rbind(
  wcs_tn, 
  wcs_per
) %>% 
  filter(jurisdiction == "Statewide") %>% 
  filter(year<2021) %>% 
  group_by(
    state_id
  ) %>% 
  filter(n_distinct(year)>1, n_distinct(jurisdiction)==1) %>% 
  mutate(
    food = food +compostable_paper+yard_waste, 
    food_lag = lag(food, n=1), 
    year_lag = lag(year, n=1)
  ) %>% 
  select(state_id, year, food, food_lag, year_lag) %>% 
  filter(!is.na(food_lag), year_lag-year <= 10) %>% 
  mutate(
    per_change = (food-food_lag)/food_lag, 
    pp_change = food-food_lag
  ) %>% ungroup%>% 
  #filter(per_change==min(per_change))
filter(abs(pp_change)==max(abs(pp_change)))

rbind(
  wcs_tn, 
  wcs_per
) %>% 
  #filter(jurisdiction == "Statewide") %>% 
  filter(year<2021) %>% filter(!state_id %in%c("MA", "VT")) %>%
  group_by(
    state_id
  ) %>% 
  filter(n_distinct(year)>1, n_distinct(jurisdiction)==1) %>% 
  mutate(
    food = food , 
    food_lag = lag(food, n=1), 
    year_lag = lag(year, n=1)
  ) %>% 
  select(state_id, year, food, food_lag, year_lag) %>% 
  filter(!is.na(food_lag), year_lag-year <= 10) %>% 
  mutate(
    per_change = (food-food_lag)/food_lag, 
    pp_change = food-food_lag
  ) %>% ungroup%>% 
  #filter(per_change==min(per_change))
filter(abs(pp_change)==max(abs(pp_change)))

rbind(
  wcs_tn, 
  wcs_per
) %>% 
  #filter(jurisdiction == "Statewide") %>% 
  filter(year<2021) %>% 
  group_by(
    state_id
  ) %>% 
  filter(n_distinct(year)>1, n_distinct(jurisdiction)==1) %>% 
  mutate(
    food = food +compostable_paper, 
    food_lag = lag(food, n=1), 
    year_lag = lag(year, n=1)
  ) %>% 
  select(state_id, year, food, food_lag, year_lag) %>% 
  filter(!is.na(food_lag), year_lag-year <= 10) %>% 
  mutate(
    per_change = (food-food_lag)/food_lag, 
    pp_change = food-food_lag
  ) %>% ungroup%>% 
  #filter(per_change==min(per_change))
filter(abs(pp_change)==max(abs(pp_change)))
  
```

### Year on Year changes 

```{r}
yty_wcs <- function (n_c)
{
  rbind(
    wcs_tn, 
    wcs_per
  ) %>% 
    filter(year>2005, year<2021)%>%
    filter(jurisdiction == "Statewide") %>% 
    mutate(
      compostable_paper = compostable_paper %>% {ifelse(is.na(.), 0, .)}
    ) %>% 
    group_by(year) %>% 
    summarise(
      food = mean(food), 
      food_comp = mean(food+compostable_paper),
      comp = mean(food+compostable_paper+yard_waste)
    ) %>% 
    pivot_longer(cols = c("food", "food_comp", "comp"), names_to = "materials", values_to = "per") %>% 
    group_by(materials) %>% 
    mutate(
      lag = lag(per, n=n_c)
    ) %>% 
    filter(!is.na(lag)) %>% 
    mutate(
      per_chane = 100*(per-lag)/lag, 
      pp_change = 100*(per-lag)
    ) %>% 
    #filter(year<2021) %>% 
    filter(abs(pp_change)==max(abs(pp_change)))
}

yty_wcs(n_c=1)
yty_wcs(n_c=2)
yty_wcs(n_c=3)
yty_wcs(n_c=4)
yty_wcs(n_c=5)

```

### Within year

```{r}

  rbind(
    wcs_tn, 
    wcs_per
  ) %>% 
    filter(year>2005, year<2021)%>%
    filter(jurisdiction == "Statewide") %>% 
    mutate(
      compostable_paper = compostable_paper %>% {ifelse(is.na(.), 0, .)}
    ) %>% 
    group_by(year) %>% 
    summarise(
      food = food%>% {max(.)-min(.)}, 
      food_comp = (food+compostable_paper)%>% {max(.)-min(.)},
      comp = (food+compostable_paper+yard_waste)%>% {max(.)-min(.)}
    ) %>% 
    pivot_longer(cols = c("food", "food_comp", "comp"), names_to = "materials", values_to = "per") %>% 
    group_by(materials) %>% 
    mutate(
      lag = lag(per, n=n_c)
    ) %>% 
    filter(!is.na(lag)) %>% 
    mutate(
      per_chane = 100*(per-lag)/lag, 
      pp_change = 100*(per-lag)
    ) %>% 
    #filter(year<2021) %>% 
    filter(abs(pp_change)==max(abs(pp_change)))
```



### Other WCS

```{r}
rbind(
  wcs_tn, 
  wcs_per
) %>% 
  filter(state_id %in% c("CA", "CT", "MA", "RI", "VT"))
```

